A thermodynamic view of dusty protoplanetary disks: axisymmetric stability

### 2016-08-26 result.tex
tiny change

For simplicity we input constant values of the midplane dust-to-gas ratio
$\epsilon_0$ and the characteristic dust thickness $\Hd$. These,
together with the perturbation wavenumber $k$, comprises main the
parameters of the linear problem. We fix the radial power-law index
for the midplane gas density to $p = -1.5$, that for the
temperature profile to $q=-1$; and set the gas disk aspect-ratio
$h_\mathrm{g}=0.05$. These are fiducial values used by 
\citet[][\citetalias{lin15} in this section]{lin15}.

>>>>

For simplicity we input constant values of the midplane dust-to-gas ratio
$\epsilon_0$ and its characteristic height $H_\epsilon$, the latter being 
specified via the dust thickness $\Hd$. 
These, together with the perturbation wavenumber $k$, comprises main the
parameters of the linear problem. We fix the radial power-law index
for the midplane gas density to $p = -1.5$, that for the
temperature profile to $q=-1$; and set the gas disk aspect-ratio
$h_\mathrm{g}=0.05$. These are fiducial values used by 
\citet[][\citetalias{lin15} in this section]{lin15}.
